Web Service Wrapping, Discovery and Consumption --- More Power to the End-User

### 2010-06-14 trunk/papers/icsoc2010/paper_sec_use_case.tex
architecture overview added
git-svn-id: https://svn.forge.morfeo-project.org/fast-fp7project@865 d8b0c59b-6544-0410-94d9-83a5658a058e

The intention of this paper was to show the advances made regarding web service discovery and consumption through the two artifacts developed as part of our research. While these artifacts may be deployed and used separately by third-party applications, they were originally developed to form the backbone of the FAST platform~\cite{hoyer2009fast}.
FAST constitutes a novel approach to application composition and business process definition from a top-down user-centric perspective. Therefore, it is aimed to allow users to create their own applications by combining different components, or building blocks, such as graphical forms and back-end services in terms of their inputs and outputs. These two components, as described in Section 3 and 4, are fully integrated and present a high cohesion the rest of the components of the FAST architecture (see Picture~\ref{pic:fast_architecture}.

[TODO: create a simple picture of the FAST architecture, highlighting these two components.]

For a better understanding of the use case, it is worth to describe a few concepts related to FAST. A Gadget is the output product, aimed to be used in a specific mashup platform. Inside FAST, the platform-independent gadget is called Screenflow, which comprises a set of domain-specific Screens connected through their pre and postconditions. A screen is the most complex building block fully functional by itself. It is composed by a form conveying the graphical interface, and a set of operators and resources binding to the back-end services.

>>>>

The intention of this paper was to show the advances made regarding web service discovery and consumption through the two artifacts developed as part of our research. While these artifacts may be deployed and used separately by third-party applications, they were originally developed to form the backbone of the FAST platform~\cite{hoyer2009fast}.
FAST constitutes a novel approach to application composition and business process definition from a top-down user-centric perspective. Therefore, it is aimed at allowing users (mainly business users at the management level, without programming experience) to create their own situational applications by visually combining different components, or building blocks, such as graphical forms and back-end services in terms of their inputs and outputs. These two components, as described in Sects. 3 and 4, are fully integrated and present a high cohesion with the rest of the components of the FAST architecture (see Fig.~\ref{fig:fast_architecture}).

\begin{figure}[ht]
  \begin{center}
    \includegraphics[width=.9\linewidth]{images/fast_architecture.png}
    \caption{Overview of the FAST architecture}
    \label{fig:fast_architecture}
  \end{center}
\end{figure}

In order to facilitate a better understanding of the use case, we will describe a number of concepts related to FAST in this section. A \emph{gadget} is the end product of the platform, aimed to be used in a specific mashup platform. Within FAST, the platform-independent gadget is called \emph{screenflow}, which comprises a set of domain-specific \emph{screens} connected through their \emph{pre-} and \emph{post-conditions}. A screen is the most complex building block fully functional by itself. It is composed by a \emph{form} conveying the graphical interface, and a set of \emph{operators} and \emph{back-end services}, wrapped into so-called \emph{service resources}.
